Common Concerns in BYOD Policies

### 2017-02-02 paper.tex
Passed IEEEs PDF eXpress formating tool.

@@

\usepackage{mdframed}
\newcommand{\todo}[1]{\marginpar{\begin{mdframed}[userdefinedwidth=1cm]\tiny\sffamily\raggedright #1\end{mdframed}}}

\newenvironment{policyrule}[1]{%
  \begin{mdframed}\footnotesize
    \noindent\textbf{\sffamily #1}:~\itshape%
  }{%
  \end{mdframed}
}

\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{microtype}

@@

A more complex example can be taken from the NHS policy.
Employees are not allowed to call non-domestic, or premium rate numbers on
company-owned phones~\footnote{The NHS policy frequently doesn't distinguish between
  company and privately owned phones and applies to both.}, however an exception can be made if approved by the appropriate manager.
To implement this we have the default rule that international calls are banned, a second rule stating that it is allowed if an exemption is made, finally a third rule delegating the exemption making process to the employee's manager.
\begin{policyrule}{NHS}
  All mobile devices will be configured for national access only. Premium/international calls will be barred.
  International call barring and roaming arrangements can be lifted for specific periods, to be stipulated on request, on approval of the relevant manager/budget holder.
  \begin{lstlisting}
'nhs-trust' says Device canCall(TelephoneNumber:X)
  if Device isOwnedBy('nhs-trust'),
     X isNationalNumber, X isStandardRateNumber.

>>>>

\usepackage[draft]{hyperref}
%\usepackage{nohyperref}
%\usepackage{url}

@@

\usepackage{mdframed}
\newcommand{\todo}[1]{\marginpar{\begin{mdframed}[userdefinedwidth=0.5cm, innerbottommargin=0]\tiny\sffamily\raggedright #1\end{mdframed}}}

\newenvironment{policyrule}[1]{%
  \begin{mdframed}[innerbottommargin=0]\footnotesize
    \noindent\textbf{\sffamily #1}:~\itshape%
  }{%
  \end{mdframed}
}

\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{microtype}

@@

A more complex example can be taken from the NHS policy.
Employees are not allowed to call non-domestic, or premium rate numbers on
company-owned phones~\footnote{The NHS policy doesn't distinguish between
  company and privately owned phones and applies to both.}, however an exception can be made if approved by the appropriate manager.
To implement this we have the default rule that international calls are banned, a second rule stating that it is allowed if an exemption is made, finally a third rule delegating the exemption making process to the employee's manager.
\begin{policyrule}{NHS}
  All mobile devices will be configured for national access only. Premium/international calls will be barred.
  International call barring and roaming arrangements can be lifted for specific periods, to be stipulated on request, on approval of the relevant manager/budget holder.
  \begin{lstlisting}
'nhs-trust' says Device canCall(TelephoneNumber:X)
  if Device isOwnedBy('nhs-trust'),
     X isNationalNumber, X isStandardRateNumber.
